### 2022-08-30 doc/src/AdvPLIC.tex

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Domain configuration (\zSafe{domaincfg})}

@@

>>>>

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection{Domain configuration (\zSafe{domaincfg})}
\label{sec:AdvPLIC-reg-domaincfg}

@@

%-----------------------------------------------------------------------
\section{Reset}

Upon reset of an APLIC, all its state becomes
valid and consistent but otherwise {\unspecified}, except for:
\begin{tightList}

\item
the \z{domaincfg} register of each interrupt domain
(Section~\ref{sec:AdvPLIC-reg-domaincfg});

\item
possibly the MSI address configuration registers of machine-level
interrupt domains (Sections \ref{sec:AdvPLIC-reg-mmsiaddrcfg}
and \ref{sec:AdvPLIC-reg-smsiaddrcfg}); and

\item
the Busy bit of each interrupt domain's \z{genmsi} register,
if it exists (Section \ref{sec:AdvPLIC-reg-genmsi}).

\end{tightList}
